### 2021-06-03 paper/model/number_of_contacts.tex
Some smallish updates; compile on Linux.

In our empirical application we distinguish the following types of contacts:

\begin{itemize}
    \item Households: Each household member meets all other household members every day.
    The household sizes and structures are calibrated to be representative for Germany.

    \item Random non-work contacts: Each person has contacts with randomly drawn other
    people which are assortative with respect to region and age group. This contact type
    reflects contacts during pure leisure activities as well as non leisure activities
    such as grocery shopping or medical appointments.

    \item Recurrent daily non-work contacts: Each person has daily recurring contacts
    which allows to model close relationships other than families between individuals.

    \item Recurrent weekly non-work contacts: Each person has weekly recurring contacts
    like sports groups or other weekly activities.

    \item Random work contacts: Each working adult has contact to randomly drawn other
    people at work.

    \item Recurrent daily work contacts: Each working adult meets other workers every
    day. This is meant to capture work colleagues.

    \item Recurrent weekly work contacts: Each working adult meets other workers once
    per week. We randomize over the days on which the meetings take place. This is meant
    to capture meetings with clients, superiors or other colleagues which happen
    infrequently.

    \item Schools: Each student meets all of his classmates every day. Class sizes are
    calibrated to be representative for Germany and students have the same age. Schools
    are closed on weekends and during vacations, which vary by states. School classes
    also meet three pairs of teachers every school day. The pairs are meant to represent
    interactions between teachers.

>>>>

In our empirical application we distinguish the following types of contacts:\comment[id=HM]{I started updating this to understand it better myself. In the end, I think it will be useful to group into HH / work / schools and add an introductory sentence for each group. E.g., that work is for everybody who is working --- except there is a different model for teachers (?), ...}

\begin{itemize}
    \item Households: Each household member meets all other household members every day.
    % Household sizes and structures are calibrated to be representative for Germany.

    \item Recurrent daily non-work contacts representing very close family or friendship
    relations outside the household.

    \item Recurrent weekly non-work contacts representing friendships, sports groups,
    charity work, or other activities. We randomize over the days on which the meetings take place.\comment[id=HM]{True?}

    \item Random non-work contacts: Contacts with randomly drawn other
    people, which are assortative with respect to region and age group. This contact type
    reflects contacts during leisure activities, grocery shopping, medical appointments,
    etc..

    \item Recurrent daily work contacts, capturing direct colleagues.

    \item Recurrent weekly work contacts, representing meetings with clients, superiors, or more distant colleagues.
    We randomize over the days on which the meetings take place.

    \item Random work contacts: Working adults' contacts with randomly drawn other
    people, which are assortative in geographical location\comment[id=HM]{True? age?}

    \item Schools: Each student meets all of his classmates every day. Class sizes are
    calibrated to be representative for Germany and students have the same age. Schools
    are closed on weekends and during vacations, which vary by states. School classes
    also meet three pairs of teachers every school day. The pairs are meant to represent
    interactions between teachers.\comment[id=HM]{Not updated from here on. Mayb}

### 2021-06-03 paper/report.tex
Some smallish updates; compile on Linux.

\section{Report}

Main contributions
\begin{itemize}
      \item Pattern: Large 2nd/3rd waves, B.1.1.7 dominant variant, steep fall in spring
      \item Many policies and developments at once: Seasonality, NPIs (private / school closures / workplace restrictions), , vaccinations, tests.
      \item Model that makes the most of many available data sources to gauge the relative effects in this transition period -- see joint distribution of infections with age, geography. But contacts with age, geography, occupations. 
      \item Intuitive -- directly work with primitives
      \item Very general approach: Limited only by size of computer and availability of data
      \item Too many policies at once for SEIR extensions
\end{itemize}

@@

\paragraph{Motivation}
\begin{itemize}
    \item CoViD-19 pandemic huge challenge. 
    \item Vaccination hold promise that will can be contained. 
    \item But most countries find themselves still many months---and often years---away from reaching herd immunity through vaccinations.
    \item Important what they do in the meantime
    \item Measures initially hard lockdown, but always crept back and not sustainable in long run
    \item Measures become increasingly diverse: Testing, Vaccination, ...
    \item Effect of seasonality unclear.
    \item Striking patterns in Europe. 
    \item Important to have models explaining the spread, which take advantage of data in a timely fashion and predict effects of interventions
\end{itemize}

>>>>

% Reports (up to ~2500 words including references, notes and captions–corresponds to ~3 printed pages in the journal) present important new research results of broad significance. Reports should include an abstract, an introductory paragraph, up to four figures or tables, and about 30 references. Materials and Methods should be included in supplementary materials, which should also include information needed to support the paper's conclusions.

\section{Main contributions}

\begin{itemize}
    \item Pattern: Large 2nd/3rd waves, B.1.1.7 dominant variant, steep fall in spring
    \item Many policies and developments at once: Seasonality, NPIs (private / school closures / workplace restrictions), , vaccinations, tests.
    \item Model that makes the most of many available data sources to gauge the relative effects in this transition period -- see joint distribution of infections with age, geography. But contacts with age, geography, occupations. 
    \item Intuitive -- directly work with primitives
    \item Very general approach: Limited only by size of computer and availability of data
    \item Too many policies at once for SEIR extensions
\end{itemize}

@@

\clearpage

Since early 2020, the CoViD-19 pandemic has presented an enormous challenge to humanity on many dimensions. The development of highly effective vaccines holds the promise of containment in the medium term. However, most countries find themselves many months---and often years---away from reaching vaccination-induced herd immunity.\comment[id=HM]{Cite some paper on herd immunity, maybe vaccine data} It is thus

\begin{itemize}
    \item Important what they do in the meantime
    \item Measures initially hard lockdown, but always crept back and not sustainable in long run. Hardly helpful on their own for more infectious strains
    \item Measures become increasingly diverse: Testing, Vaccination, ...
    \item Effect of seasonality unclear.
    \item Striking patterns in Europe. 
    \item Important to have models explaining the spread, which take advantage of data in a timely fashion and predict effects of interventions
\end{itemize}
